\textsf{Are large language models superhuman chemists?}

### 2024-10-28 src/tex/appendix.tex
fix: solve formatting problems in examples table

%    \caption{\textbf{Examples for each of the topics considered in the evaluation of the \chembench corpus.} The table shows the percentage of questions in the corpus that belong to each topic, as well as example questions.}
%    \label{tab:chembench_corpus_topic}
%            \multicolumn{1}{c}{\textbf{Analytical Chemistry} 166 Questions (5.8\%)} \\
%            Which of the following analytical methods is most appropriate for performing a survey analysis of a solid sample containing various metals? \\
%            A. X-ray fluorescence analysis \\
%            B. Differential pulse polarography \\
%            C. Flame-atomic absorption spectroscopy \\
%            D. Gas chromatography with flame ionization detector \\
%            E. Hydride generation atomic absorption spectroscopy \\
%            \multicolumn{1}{c}{\textbf{Chemical Preference} 1001 Questions (35\%)} \\
%            \multicolumn{1}{c}{\textbf{General Chemistry} 152 Questions (5.3\%)} \\
%            Which of the following salts is an acidic salt? \\
%            A. \ce{NH4Cl} \\
%            B. \ce{Na2CO3} \\
%            C. \ce{NaH2PO4} \\
%            D. \ce{Zn(OH)Cl} \\
%            \multicolumn{1}{c}{\textbf{Inorganic Chemistry} 94 Questions (3.3\%)} \\
%            What is the oxidation number of the metal in the compound \ce{[ZrF7]^{3-}}\\
%            \multicolumn{1}{c}{\textbf{Materials Science} 89 Questions (3.1\%)} \\
%            For NMR analysis, you need to digest the MOF in a strong acid to remove the linker and leave the metal clusters intact. Why would one choose \ce{HF} over \ce{HCl} for this purpose? \\
%            A. \ce{F-} forms a stable bonds to the metal ions \\
%            B. \ce{HF} has a better water solubility than \ce{HCl} \\
%            C. \ce{HF} has a higher boiling point than \ce{HCl} \\
%            D. \ce{HF} is a weaker acid than \ce{HCl} \\
%            \multicolumn{1}{c}{\textbf{Organic Chemistry} 441 Questions (15.5\%)} \\
%            What is the reaction mechanism that describes the following reaction (represented using reaction SMILES) [START\_RXNSMILES]CCCl.CO[Na]>>[Na]Cl.CCOC\-[END\_RXNSMILES]? \\
%            A. $E_1$ \\
%            B. $E_{cb}$ \\
%            C. $S_N1$ \\
%            D. $S_N2$ \\
%            \multicolumn{1}{c}{\textbf{Physical Chemistry} 179 Questions (6.3\%)} \\
%            The Born-Oppenheimer (BO) approximation is widely used in computational chemistry, but its accuracy can vary depending on the system. Among the following options, for which system is the Born-Oppenheimer approximation likely to be least applicable? \\
%            A. \ce{C60} \\
%            B. \ce{CH4} \\
%            C. \ce{Fe(CO)5} \\
%            D. \ce{H2+} \\
%            E. \ce{NaCl} \\
%            \multicolumn{1}{c}{\textbf{Technical Chemistry} 42 Questions (1.5\%)} \\
%            Which of the following statements is true about the different types of ideal reactors? \\
%            A. In a batch reactor, the composition is uniformly mixed and remains the same throughout the reactor and at the exit \\
%            B. In a batch reactor, the fluid passes through the reactor with no mixing of earlier and later entering fluid \\
%            C. In a mixed flow reactor, the composition changes with time but is uniform everywhere within the reactor \\
%            D. In a plug flow reactor, the fluid moves in single flow through the reactor with no mixing and no overtaking \\
%            \multicolumn{1}{c}{\textbf{Toxicity/Safety} 690 Questions (24.2\%)} \\
%            Pindolol and propranolol are (relatively nonselective) antagonists at $\beta_1$- and $\beta_2$-adrenoceptors. However, pindolol is a partial agonist, whereas propranolol is a pure antagonist. What follows from this? \\
%            A. Pindolol has a greater therapeutic range than propranolol \\
%            B. Pindolol has a longer half-life than propranolol \\
%            C. Pindolol has intrinsic activity \\
%            D. Pindolol is more lipophilic than propranolol \\
%            E. Pindolol is more potent than propranolol \\

@@

To better understand the cognitive demands of chemical assessment, we categorized the questions in the ChemBench corpus according to the primary skills required to solve them. The table \Cref{tab:chembench_corpus_models_failed_cognitive} below shows representative examples of questions that state-of-the-art models failed to answer correctly across different cognitive skill categories, including knowledge, reasoning and intuition.
\begin{table}
    \centering
    \small
    \caption{\textbf{Examples of required skills evaluated in the \chembench corpus that the state-of-the-art model failed to answer correctly} The table displays the number of questions for each skill, along with an example question that the model failed to answer.}
    \label{tab:chembench_corpus_models_failed_cognitive}
    {\fontsize{8}{9}\selectfont
        \begin{tabularx}{\textwidth}{X}
            \toprule
            \multicolumn{1}{c}{\textbf{Knowledge} 919 Questions} \\
            \midrule
            Which of the following are true for phosphoric acid? \\
            A. Is a weak acid, so it is not toxic \\
            B. Should never be tasted \\
            C. Though a component of soft drinks, reacts vigorously with water when in concentrated form \\
            \midrule
            \multicolumn{1}{c}{\textbf{Reasoning} 987 Questions} \\
            \midrule
            Which of the following elements has the largest atomic radius? \\
            A. \ce{Fr} \\
            B. \ce{He} \\
            C. \ce{Li} \\
            D. \ce{Rb} \\
            \midrule
            \multicolumn{1}{c}{\textbf{Intuition} 1001 Questions} \\
            \midrule
            Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
            A. [START_SMILES]CCc1c(CCOC)nn(-c2ccccc2)c1-c1ccccc1[END_SMILES] \\
            B. [START_SMILES]Cc1cc(/C=C2\\C(=N)N3N=C(S(C)(=O)=O)SC3=NC2=O)c(C)n1Cc1ccccc1[END_SMILES] \\
            \midrule
            \multicolumn{1}{c}{\textbf{Calculation} 128 Questions} \\
            \midrule
            The cell potential for the overall cell reaction during electrolysis of water, \ce{2H2O(l) -> 2H2(g) + O2(g)} is \SI{-1.23 V}. What is the standard electrode potential for the half reaction, \ce{2H2O(l) -> O2(g) + 4H+(aq) + 4e-} in V? \\
            \bottomrule
        \end{tabularx}
    }
\end{table}

>>>>

\begin{table}
    \centering
    \small
    \caption{\textbf{Examples for each of the topics considered in the evaluation of the \chembench corpus.} The table shows the percentage of questions in the corpus that belong to each topic, as well as example questions.}
    \label{tab:chembench_corpus_topic}
    {\fontsize{8}{9}\selectfont
        \begin{tabularx}{\textwidth}{X}
            \toprule
            \multicolumn{1}{c}{\textbf{Analytical Chemistry} 166 Questions (5.8\%)} \\
            \midrule
            Which of the following analytical methods is most appropriate for performing a survey analysis of a solid sample containing various metals? \\
            A. X-ray fluorescence analysis \\
            B. Differential pulse polarography \\
            C. Flame-atomic absorption spectroscopy \\
            D. Gas chromatography with flame ionization detector \\
            E. Hydride generation atomic absorption spectroscopy \\
            \midrule
            \multicolumn{1}{c}{\textbf{Chemical Preference} 1001 Questions (35\%)} \\
            \midrule
            Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
            A. [START\_SMILES]N\#Cc1ccc(OCCCN2CC3CN\-(CCNS(=O)(=O)c4ccc(F)cc4)CC(C2)O3)cc1\-[END\-\_SMILES] \\
            B. [START\_SMILES]O=C1CC(c2ccc(CC(NS(=O)\-(=O)\-c3cc(Cl)cc(Cl)c3)c3nc4ccccc4[nH]3)cc2)S\-(=O)\-(=O)N1[END\_SMILES] \\
            \midrule
            \multicolumn{1}{c}{\textbf{General Chemistry} 152 Questions (5.3\%)} \\
            \midrule
            Which of the following salts is an acidic salt? \\
            A. \ce{NH4Cl} \\
            B. \ce{Na2CO3} \\
            C. \ce{NaH2PO4} \\
            D. \ce{Zn(OH)Cl} \\
            \midrule
            \multicolumn{1}{c}{\textbf{Inorganic Chemistry} 94 Questions (3.3\%)} \\
            \midrule
            What is the oxidation number of the metal in the compound  \ce{[ZrF_{7}]3-} \\
            \midrule
            \multicolumn{1}{c}{\textbf{Materials Science} 89 Questions (3.1\%)} \\
            \midrule
            For NMR analysis, you need to digest the MOF in a strong acid to remove the linker and leave the metal clusters intact. Why would one choose HF over \ce{HCl} for this purpose? \\
            A. \ce{F-} forms a stable bonds to the metal ions \\
            B. \ce{HF} has a better water solubility than \ce{HCl} \\
            C. \ce{HF} has a higher boiling point than \ce{HCl} \\
            D. \ce{HF} is a weaker acid than \ce{HCl} \\
            \midrule
            \multicolumn{1}{c}{\textbf{Organic Chemistry} 441 Questions (15.5\%)} \\
            \midrule
            What is the reaction mechanism that describes the following reaction (represented using reaction SMILES) [START\_RXNSMILES]CCCl.CO[Na]>>[Na]Cl.CCOC\-[END\_RXNSMILES]? \\
            A. $E_1$ \\
            B. $E_{cb}$ \\
            C. $S_N1$ \\
            D. $S_N2$ \\
            \midrule
            \multicolumn{1}{c}{\textbf{Physical Chemistry} 179 Questions (6.3\%)} \\
            \midrule
            The Born-Oppenheimer (BO) approximation is widely used in computational chemistry, but its accuracy can vary depending on the system. Among the following options, for which system is the Born-Oppenheimer approximation likely to be least applicable? \\
            A. \ce{C60} \\
            B. \ce{CH4} \\
            C. \ce{Fe(CO)5} \\
            D. \ce{H2+} \\
            E. \ce{NaCl} \\
            \midrule
            \multicolumn{1}{c}{\textbf{Technical Chemistry} 42 Questions (1.5\%)} \\
            \midrule
            Which of the following statements is true about the different types of ideal reactors? \\
            A. In a batch reactor, the composition is uniformly mixed and remains the same throughout the reactor and at the exit \\
            B. In a batch reactor, the fluid passes through the reactor with no mixing of earlier and later entering fluid \\
            C. In a mixed flow reactor, the composition changes with time but is uniform everywhere within the reactor \\
            D. In a plug flow reactor, the fluid moves in single flow through the reactor with no mixing and no overtaking \\
            \midrule
            \multicolumn{1}{c}{\textbf{Toxicity/Safety} 690 Questions (24.2\%)} \\
            \midrule
            Pindolol and propranolol are (relatively nonselective) antagonists at $\beta_1$- and $\beta_2$-adrenoceptors. However, pindolol is a partial agonist, whereas propranolol is a pure antagonist. What follows from this? \\
            A. Pindolol has a greater therapeutic range than propranolol \\
            B. Pindolol has a longer half-life than propranolol \\
            C. Pindolol has intrinsic activity \\
            D. Pindolol is more lipophilic than propranolol \\
            E. Pindolol is more potent than propranolol \\
            \bottomrule
        \end{tabularx}
    }
 \end{table}

@@

% \normalsize

% To better understand the cognitive demands of chemical assessment, we categorized the questions in the ChemBench corpus according to the primary skills required to solve them. The table \Cref{tab:chembench_corpus_models_failed_cognitive} below shows representative examples of questions that state-of-the-art models failed to answer correctly across different cognitive skill categories, including knowledge, reasoning and intuition.
% \begin{table}
%     \centering
%     \small
%     \caption{\textbf{Examples of required skills evaluated in the \chembench corpus that the state-of-the-art model failed to answer correctly} The table displays the number of questions for each skill, along with an example question that the model failed to answer.}
%     \label{tab:chembench_corpus_models_failed_cognitive}
%     {\fontsize{8}{9}\selectfont
%         \begin{tabularx}{\textwidth}{X}
%             \toprule
%             \multicolumn{1}{c}{\textbf{Knowledge} 919 Questions} \\
%             \midrule
%             Which of the following are true for phosphoric acid? \\
%             A. Is a weak acid, so it is not toxic \\
%             B. Should never be tasted \\
%             C. Though a component of soft drinks, reacts vigorously with water when in concentrated form \\
%             \midrule
%             \multicolumn{1}{c}{\textbf{Reasoning} 987 Questions} \\
%             \midrule
%             Which of the following elements has the largest atomic radius? \\
%             A. \ce{Fr} \\
%             B. \ce{He} \\
%             C. \ce{Li} \\
%             D. \ce{Rb} \\
%             \midrule
%             \multicolumn{1}{c}{\textbf{Intuition} 1001 Questions} \\
%             \midrule
%             Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
%             A. [START\_SMILES]CCc1c(CCOC)nn(-c2ccccc2)c1-c1ccccc1[END\_SMILES] \\
%             B. [START\_SMILES]Cc1cc(/C=C2\\C(=N)N3N=C(S(C)(=O)=O)SC3=NC2=O)c(C)n1Cc1ccccc1[END\_SMILES] \\
%             \midrule
%             \multicolumn{1}{c}{\textbf{Calculation} 128 Questions} \\
%             \midrule
%             The cell potential for the overall cell reaction during electrolysis of water, \ce{2H2O(l) -> 2H2(g) + O2(g)} is \SI{-1.23}{V}. What is the standard electrode potential for the half reaction, \ce{2H2O(l) -> O2(g) + 4H+(aq) + 4e-} in V? \\
%             \bottomrule
%         \end{tabularx}
%     }
% \end{table}
